### 2024-06-13 output/manuscript.tex
Updated

\documentclass[12pt]{article}

\usepackage{ediArticle}  %from ediArticle.sty

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\LARGE \bfseries \vspace{-1cm} Just Another Latex Template \\
    \LARGE \normalfont Research Proposal}
\author{\Large \textit{Edifofon Akpan}}
\date{ }

\begin{document}

% Set font size to 13pt
\fontsize{13pt}{15pt}\selectfont

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Lorem ipsum dolor sit amet

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
Lorem ipsum dolor sit amet

\hspace{1em}

\begin{table}[H]
    \centering 
    \caption{The facts about lorem ipsum generator from online sources.}
    \begin{tabular}{|C{2cm}|L{10cm}|C{2.5cm}|}
        \hline
        \PlainInput{tables/tab_1}
    \end{tabular}
    \label{MyTable1}
    \caption*{\footnotesize \textit{Notes:} Donec sit amet viverra justo. Duis malesuada velit}
\end{table}

\section{Results}
Lorem ipsum dolor sit amet (\autoref{MyTable1}).

\hspace{1em}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\linewidth]{figures/figure.png}
    \caption{The facts about lorem ipsum generator from online sources.}
    \label{fig:enter-label}
    \caption*{\footnotesize \textit{Notes:} Lorem ipsum dolor sit amet}
\end{figure}

\section{Discussion}
Lorem ipsum dolor sit amet.\parencite{akpan_cost-effectiveness_2022}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% %%%
%%% Bibliography %%%

\clearpage
\newrefcontext[sorting=nyt]
\printbibliography

\end{document}

### 2024-06-13 code/analysis.R
Updated

@@ -1,0 +1,300 @@
+# Import studies from folder
+studies <- read.csv("data/studies.csv", row.names=NULL, stringsAsFactors=TRUE)
+
+
+
+# *Create sum of # published articles per year
+# sort pubyear studyid
+# 
+# gen studydecisionBin = studythresholddecision
+# recode studydecisionBin 3=0 2=1
+# 
+# gen ochalekhighdecisionBin = ochalekhighdecision
+# recode ochalekhighdecisionBin 3=0 2=1
+# 
+# gen ochaleklowdecisionBin = ochaleklowdecision
+# recode ochaleklowdecisionBin 3=0 2=1
+# 
+# gen woodshighdecisionBin = woodshighdecision
+# recode woodshighdecisionBin 3=0 2=1
+# 
+# gen woodslowdecisionBin = woodslowdecision
+# recode woodslowdecisionBin 3=0 2=1
+# 
+# label define DECISIONBin 0 "Not Cost-Effective" 1 "Cost-Effective"
+# label values studydecisionBin ochalekhighdecisionBin ochaleklowdecisionBin woodshighdecisionBin woodslowdecisionBin DECISIONBin
+# 
+# 
+# 
+# *ICER 999999 means dominated (there are 4 such evals) 
+# *careful with negative ICERs (cost-saving)
+# 
+# 
+# 
+# ********************** Table 1 *****************************
+#   //net install table1_mc.pkg
+# table1_mc, vars(comparisonCat cat %5.0f\ dosenumCat cat %5.0f \ perspective bin %5.0f \ income cat %5.0f \ herdeffects cat %5.0f \ seroreplace cat %5.0f \ efficacyotitis cat %5.0f \ budgetimpact cat %5.0f)  onecol slashN
+# 
+# 
+# // unique articles by study characteristics
+# //ssc inst unique
+# unique studyid, gen(totstud) by(icerid)
+# drop totstud
+# unique studyid, gen(totstud) by(pubyear)
+# drop totstud
+# unique studyid, gen(totstud) by(comparisonCat)
+# drop totstud
+# unique studyid, gen(totstud) by(dosenumCat)
+# drop totstud
+# unique studyid, gen(totstud) by(perspective)
+# drop totstud
+# unique studyid, gen(totstud) by(income)
+# drop totstud
+# unique studyid, gen(totstud) by(country)
+# drop totstud
+# unique studyid, gen(totstud) by(herdeffects)
+# drop totstud
[…]

### 2024-06-13 output/manuscript.tex
Updated
Updates from Overleaf

@@
 
-\usepackage{ediArticle}  %from ediArticle.sty
+\usepackage{latex/ediArticle}  %from ediArticle.sty
 
@@
 \section{Introduction}
-Lorem ipsum dolor sit amet
+
+[Not started – outline only below]
+-	Pneumococcal disease burden globally (and trend over time), 
+-	Availability of effective and safe vaccines; PCVs recommended by WHO; But costly compared to most childhood vaccines 
+-	Introduction/coverage of these vaccines: High use in high income and many low-income countries… trend in roll out over time. Lagging middle-income countries, those lacking Gavi/AMC eligibility.
+-	PCV  introduction guided by HTA processes in many LMICs.
+Ex Thailand, Philippines, China.
+In other settings ex Pacific islands, no HTA processes available – based on donor or development partner support
+
+-	One component of HTA is cost-effectiveness analysis: CEA is method for weighing costs and outcomes in comparable method across interventions – provides guidance on value for money of new technologies.
+Results are typically presented as incremental cost-effectiveness ratios, in \$/QALY gained or \$/DALY averted.
+If a vaccine is found to be cost-saving, usually implemented pending other factors (budget impact, political and equity considerations, and other practical and logistical considerations including availability of vaccine, etc).
+Vaccines that are not cost-saving, but result in higher costs and higher health benefits, are often compared to country-specific willingness to pay thresholds, to determine whether an intervention is considered cost-effective, or good value for money.
+
+-	Recent systematic reviews1-4 PCV is CE across (most)( LMICs (sometimes cost-saving).
+Cost-effectiveness is influenced by vaccine price (local acquisition), inclusion/exclusion of indirect effects (serotype replacement and herd effects), cross protection, disease burden (Incidence / mortality from IPD and pneumonia), and vaccine efficacy and coverage
+-	Where are we at with willingness to pay thresholds in LMICs?
+Historically thresholds of 1-3 x gross domestic product (GDP) per capita have been used to assess the cost-effectiveness of vaccines and other interventions in low- and middle-income countries .
+Others thresholds have existed but unclear the origins of these, and what they are based on.
+
+-	Newer  country-specific estimates 2-3 of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
+New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
+Several countries are in process of developing these thresholds (ex: Indonesia ).
+New estimates from \textcite{woods_country-level_2016} (based on 1 empirical estimate from a high-income setting) and \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs) and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
+(Woods also provides this for high income settings).
+
+-	Despite the World Health Organization and others recommending against using GDP per capita-based thresholds for judging the value for money of healthcare interventions most recent studies continue to do so4.
+Recent systematic review of 230 studies (713 interventions) published CEAs in LMICs: 1-3 × GDP/ capita was the most common type of threshold used (84.3\%) ; ~ A third of studies (34.2\%) using 1 to 3× GDP per capita applied a threshold at 3× GDP per capita.
+No study used locally developed thresholds.
+79.3\% of interventions received a recommendation as “cost-effective”.
+-	What do new(er) thresholds mean for previously published CEAs?
+
+The aim of this study is to investigate whether new country-specific estimates on cost-effectiveness thresholds (CET) based on health opportunity costs may impact on study conclusions about the cost-effectiveness of pneumococcal conjugate vaccine programs in low- and middle-income countries.
+A secondary aim is to investigate which study factors are influential in driving study conclusions that switch from finding PCV to be cost-effective to not cost-effective.
 
@@
 \section{Methods}
-Lorem ipsum dolor sit amet
+\subsection{Systematic Literature Review}
+We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.1 We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-benefit OR cost-utility OR cost-effectiveness OR cost-benefit OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 25 April 2022.
+The search was limited to low- and middle-income countries (LMICs) using country names and related LMIC terminology (see Appendix 1 in Supplementary Material).
+We also checked published systematic reviews on economic evaluation of PCV for additional studies.1-4
+
+All identified titles and abstracts were screened by one author (EA) to remove studies that were clearly not related to the topic, were not primary research, or not focused on a LMIC.
+Two reviewers (EA, NC) independently screened the full text of studies remaining against seven inclusion criteria: (1) original articles containing a full economic evaluation (two evaluations, costs and consequences ),5 (2) focused on one or more LMICs, (3) evaluated PCV covering seven or more serotypes, (4) evaluated PCV in children less than 12 years, (5) used either disability-adjusted life-years (DALYs), quality-adjusted life years (QALYs) or life-years (LY), as outcome measure, (6) reported an incremental cost-effectiveness ratio (ICER) and (7) were in English.
+Editorials, letters, conference or meeting abstracts or proceedings, and review articles were excluded.
+Multi-country studies not reporting country-specific ICERs were also excluded.
+Evaluations of pneumococcal polysaccharide vaccine were excluded.
+
+The following data were extracted by one reviewer (EA) into an Excel data extraction template: study characteristics (country, currency and cost year, World Bank country income group, vaccine evaluated and comparator, number and unit price of doses); methodological assumptions of cost-effectiveness analysis (perspective (societal or healthcare payer), time horizon, discount rate, and considerations of herd effects (with or without) and serotype replacement (with or without)); and study results (outcome measure, ICER for each evaluation where this was separately reported (by perspective, and by inclusion or exclusion of herd effects and by serotype replacement, where possible), inclusion of budget impact (yes or no), cost-effectiveness threshold used and conclusion on cost-effectiveness, for each evaluation ).
+A second reviewer (NC) double-extracted one-third of studies.
+Any inconsistencies were discussed resolved in consultation with both reviewers.
+The extracted data was compared with data from published systematic reviews1-4 to verify the extracted data on study characteristics, parameters and ICERs.
+
+Risk of bias was not assessed as this has been done by previously published systematic reviews2 and was not the focus of the current review.
+
+\subsubsection{Data Preparation}
+Countries were classified by World Bank country income group as upper middle (UM), lower middle (LM), and low (L) income.
+Where reported in a different currency, ICERs and vaccine dose prices were converted to United States dollars (USD) using year- and currency-specific exchange rates from the World Bank.6 Country- and year-specific GDP per capita estimates (in USD) were compiled from World Bank data and used to convert ICERs for all evaluations into a \% GDP per capita.
+We extracted country-specific upper- and lower-bound CETs from the Woods7 and Ochalek8 studies, in terms of \% GDP per capita, using the highest and lowest estimates from both studies.
+We then generated updated study conclusions (“cost-saving”, “cost-effective” or “not-cost-effective) for each evaluation according to the Woods and Ochalek CETs, by comparing the converted ICER (in \% GDP per capita) to the upper- and lower-bound CETs (in \% GDP per capita ).
+We generated four indicator variables to indicate whether study conclusions shifted from being “cost-effective” based on study specific threshold and conclusion, to “not cost-effective” (based on each of the four updated CET estimates: WoodsHigh, WoodsLow, OchalekHigh, OchalekLow).
+Studies where CETs were not explicitly stated were not included in the statistical analysis.
+
+\subsection{Statistical Analysis}
+We first summarised the key characteristics of studies and unique evaluations included in the review including distribution of CETs used and study conclusions.
+We then conducted a descriptive analysis of the evaluations that switched from being considered “cost-effective” by the study conclusion to “not cost-effective” (across any of the 4 CETs), by study perspective, type of comparison, income group, considerations of herd effects or serotype replacement, vaccine dose price by income group.
+
+Next, we conducted two-sample tests of differences in vaccine dose price, country income group, perspective of analysis, and considerations of herd immunity  or serotype replacement among evaluations that switched from being cost-effective across any of the 4 CETs, compared to those that didn’t switch.
+
+A series of probit regressions (one for each of the Woods and Ochalek upper and lower-bound CETs) were performed, with the outcome of interest the switch variables indicating whether an evaluation shifted from being considered cost-effective to not cost-effective using the updated CETs.
+Independent variables included in the regressions were perspective, country income group, herd immunity, and serotype replacement as categorical variables, and vaccine dose price as a continuous variable.
+
+Analyses were performed using Microsoft Excel (Microsoft Corporation, 2023) and Stata version 17.0 SE (StataCorp 2021).
 
@@
         \hline
-        \PlainInput{tables/tab_1}
+        \PlainInput{tables/char-included-studies}
     \end{tabular}
@@
 \section{Results}
-Lorem ipsum dolor sit amet (\autoref{MyTable1}).
+\subsection{Study Sample and Selection}
+The systematic search from databases returned 863 articles.
+After excluding duplicates, 375 abstracts were screened and the full-text of 78 articles were evaluated.
+Of these, 55 articles met the inclusion criteria and were included.9-63 Two (2) additional studies64,65 were identified from the reference list of the previous systematic reviews, yielding a total of 57 studies published between 2008-2022 for data extraction (see  Figure 1 for the PRISMA flowchart).
 
-\hspace{1em}
+\subsection{Characteristics of Included Studies}
+Characteristics of the 57 included studies representing 196 evaluations are presented in Table 1.
+Of the 57 studies, 44 studies contributed to more than one evaluation  since they presented ICERs for a base case or scenario analysis for different countries, vaccine comparisons, perspectives, number of doses, or including or excluding herd effects.
+Most evaluations compared PCV10 (n=74 evaluations from 30 studies), PCV13 (n=61 evaluations from 28 studies) or PCV7 (n=24 evaluations from 14 studies) to no vaccination.
+A further 27 evaluations from 19 studies compared PCV13 to PCV10, while ten evaluations from six studies included other evaluations (PCV9 vs no vaccination, PCV13 vs PCV7, and PCV10 vs PCV7).
+Most evaluations considered three (53\%) or four doses (38\%).
+Most evaluations were conducted in upper-middle income countries (n=144 or 73\%), followed by lower-middle income (n=34) and low-income (n=18) countries.
+Slightly more evaluations adopted a healthcare or payer perspective (54\%) over a societal perspective (46\%).
+Out of the 57 unique studies, 14 included both perspectives in the base case or a scenario analysis.
+Herd immunity was considered in 32\% of evaluations (n=62 from 25 studies); and serotype replacement in 15\% (n=29 evaluations from 13 studies).
+
+\subsection{Descriptive results}
+[In progress]
+Vaccine dose price and the range of dose price used in evaluations increased with increasing income level (mean (sd) \$3.94 (1.92) for L, \$14.54 (9.65) for LM, \$36.40 (33.90)  for UM income countries).
+Among evaluations with conclusions on cost-effectiveness, most (87\%) were found to be cost-effective (n=150) or cost-saving (n=20) and n=26 were not cost-effective when applying the thresholds originally used in the paper .
+In contrast, only 53-64\% (n=94 to 112) or 25-61\% (n=42-104) evaluations were considered cost-effective using the lower- or upper-bound opportunity cost estimates from the Ochalek 2018 or Woods 2016 studies, respectively.
+(Table 2)
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{figures/figure.png}
+    \includegraphics[width=1\linewidth]{output/figures/dose-price-income.png}
     \caption{The facts about lorem ipsum generator from online sources.}
@@
 
+\subsection{Factors associated with switching from cost-effective to not cost-effective}
+[In progress]
+Descriptively, evaluations that switched from being cost-effective to not cost-effective under any of the updated CETs were more likely to be comparisons between PCV7 versus no vaccination or PCV10 versus no vaccination.
+They were also more likely to be conducted in lower income settings, not to consider herd immunity, but to consider serotype replacement .
+None of these associations were statistically significant according to the Pearson Chi squared test.
+No relationship was found between perspective of analysis and the evaluation switching from begin cost-effective.
+However, evaluations that switched from being cost-effective to not cost-effective across any of the new CETs had statistically higher mean vaccine dose price: \$31.82 (\$26.73-\$36.91) vs \$15.41 (\$7.26-\$23.55).
+Probit regression results found vaccine dose price and country income group were the only statistically significant variables related to evaluations switching from being cost-effective to not cost-effective across any one of the updated CETs.
+
+\subsection{Sensitivity Analyses}
+[In progress]
+
 \section{Discussion}
-Lorem ipsum dolor sit amet.\parencite{akpan_cost-effectiveness_2022}
+\subsection{Interpretation of Results}
+[In progress]
+
+\subsection{Strengths and Limitation}
+Multi-country studies.66-69 why don't they report at country-level – this would be useful !
+[In progress by Natalie]
+Strength: first paper to our knowledge to consider the impact of new, lower CETs on conclusions of cost-effectiveness across LMICs
+Limitation: only considering base case ICERs, and ICERs available by differing perspective (health care payer vs societal), and with or without herd effects and/or serotype replacement.
+Do not include all ICERs reported by studies (ex: through sensitivity or scenario analyses exploring different vaccine dose prices etc)
+
+Compare results with countries that have or have not introduced PCV.
+Goal is not to suggest PCV should not be introduced or should be removed if not CE .
+But introducing a technology/vaccine when ICER exceeds WTP could be detrimental – money could be better spent on other things .
+Goal – to revisit cost-effectiveness and understand whether further price negotiations are necessary . Examples of price negotiations from other settings (Indonesia? Thailand?? Ask Sarin and Itob).
+
+To do later:
+Among low-income countries, xYZ 
+Among middle-income countries – what trends do we see and does that vary by vaccine price and/or taking herd effects into account?
+-	CETs are likely to vary over time, which has not been considered here
+-	Further analyses to look at associations between shifts in decision-making and characteristics of evaluations.
+-	Further work could link these evaluations to actual policy decisions in countries to introduce PCV (or not)
+Implications for PCV Policy
+[In progress]
 

### 2024-06-30 output/manuscript.tex
Updates from Overleaf

@@
 \usepackage{latex/ediArticle}  %from ediArticle.sty
+\usepackage{amsmath}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{\LARGE \bfseries \vspace{-1cm} Just Another Latex Template \\
-    \LARGE \normalfont Research Proposal}
-\author{\Large \textit{Edifofon Akpan}}
-\date{ }
+% Settings for the author block
+\usepackage{authblk}
+\usepackage{ragged2e}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% left align title, authors, and affiliations
+\makeatletter
+\renewcommand\maketitle{\par
+  \begingroup
+    \flushleft
+    \LARGE \setstretch{1.1} {\@title}\par
+  \endgroup
+  \vspace{-0.2em}
+  \begin{flushleft}
+    \large \setstretch{1.1} \@author
+  \end{flushleft}
+}
+\makeatother
+\renewcommand\Affilfont{\small \itshape}
+
+\title{Reassessing the cost-effectiveness of pneumococcal conjugate vaccines in low- and middle-income countries using opportunity cost-based thresholds}
+\author[1,*]{Natalie Carvalho, PhD}
+\author[1,2]{Edifofon Akpan, MPH}
+\author[3,4]{Fiona Russell, PhD}
+\author[5]{Mark Jit, PhD}
+\affil[1]{Centre for Health Policy, Melbourne School of Population and Global Health, The University of Melbourne, Australia.}
+\affil[2]{Sheffield Centre for Health and Related Research, School of Medicine and Population Health, The University of Sheffield, United Kingdom.}
+\affil[3]{Department of Infection and Immunity, Murdoch Children's Research Institute, Royal Children's Hospital, Australia.}
+\affil[4]{Department of Paediatrics, The University of Melbourne, Australia.}
+\affil[5]{Department of Infectious Disease Epidemiology, Faculty of Epidemiology and Population Health, London School of Hygiene and Tropical Medicine, United Kingdom.}
+\affil[*]{Corresponding author: natalie.carvalho@unimelb.edu.au; +613 8344 3715}
+
+\date{}
 
@@
 \maketitle
+\textit{Funding/support:}
+This study was supported by the Australian government National Health and Medical Research Council (NHMRC) Centre of Research Excellence for Pneumococcal Disease Control in the Asia-Pacific.
 
+\textit{Financial disclosure:} None reported.
+
+\textit{Précis:} Some pneumococcal conjugate vaccine programs in low- and middle-income countries may not be considered cost-effective under recently proposed thresholds
+
+\textit{Acknowledgments:} Samuel Grant for assistance with literature review and data extraction.
+
+\textit{Word count:} X,XXX %(excluding abstract, references, figure legends, tables, appendices)
+
+\textit{Number of pages:} X %Total number of pages (including figures, tables, appendices, etc) of the article
+
+\textit{Number of figures:} 3 %Total number of figures (including figure parts [i.e., 1a, 1b, 1c = 3]) in the main article (figures in appendices should be counted separately) Maximum 6 illustrations (tables + figures)
+
+\textit{Number of tables:} 5 %Total number of tables in the main article (tables in appendices should be counted separately)
+
+\textit{Supplementary material:} X Pages; X Figures; X Tables
+
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section*{Abstract}
+
+\textit{Objectives:} To analyse whether the adoption of recently proposed cost-effectiveness thresholds (CETs) based on health opportunity costs, change cost-effectiveness analysis (CEA) conclusions for pneumococcal conjugate vaccine (PCV) programs in low- and middle-income countries (LMICs).
+
+\textit{Methods:} We conducted a systematic literature review to identify all infant PCV CEAs conducted in LMICs.
+CEAs that considered quality-adjusted life years, disability-adjusted life years or life years as outcome measure, were published in English, in a scientific journal, and included an incremental cost-effectiveness ratio and cost-effectiveness conclusion were included.
+We re-assessed cost-effectiveness conclusions using recent upper- and lower-bound CET estimates from two sources.
+We evaluated factors associated with evaluations that switched from being cost-effective to no longer being cost-effective.
+
+\textit{Results:} We identified 57 studies containing 196 unique evaluations across 29 LMICs.
+Most studies (n=51) used a CET of 1-3x gross domestic product (GDP) per capita.
+Most evaluations (87\%) were found to be cost-effective (n=150) or cost-saving (n=20).
+Only 41\% (n=80) of evaluations remained cost-effective across all four updated CETs.
+Evaluations that switched were more likely to be comparisons of PCV7 versus no vaccination or PCV10 versus no vaccination, more likely to be conducted in lower-income settings, less likely to consider herd effects but more likely to consider serotype replacement, and had higher mean vaccine dose price among upper-middle income countries.
+Income group and vaccine dose price were the only statistically significantly factors related to evaluations that switched.
+
+\textit{Conclusions:} Under recently proposed CETs, reductions in vaccine dose price may be necessary to ensure cost-effectiveness of PCV programs.
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Highlights}
+Authors should identify 2–3 "Highlights" that illustrate the paper's contribution to the field. 
+\begin{itemize}
+    \item What is already known about the topic?
+    \item What does the paper add to existing knowledge?
+    \item What insights does the paper provide for informing healthcare-related decision making?
+\end{itemize}
+
+\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Introduction}
 
@@
 
--	Newer  country-specific estimates 2-3 of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
+Newer  country-specific estimates 2-3 of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
 New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
 Several countries are in process of developing these thresholds (ex: Indonesia ).
-New estimates from \textcite{woods_country-level_2016} (based on 1 empirical estimate from a high-income setting) and \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs) and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
-(Woods also provides this for high income settings).
+New estimates from \textcite{woods_country-level_2016} (based on 1 empirical estimate from a high-income setting), \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs), and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
+\textcite{woods_country-level_2016} also provides these estimates for high-income countries.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methods}
-\subsection{Systematic Literature Review}
-We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.1 We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-benefit OR cost-utility OR cost-effectiveness OR cost-benefit OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 25 April 2022.
+\section*{Methods}
+\subsection*{Systematic search}
+We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.\supercite{saokaew_cost_2016} We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-benefit OR cost-utility OR cost-effectiveness OR cost-benefit OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 25 April 2022.
 The search was limited to low- and middle-income countries (LMICs) using country names and related LMIC terminology (see Appendix 1 in Supplementary Material).
@@
 
-\subsubsection{Data Preparation}
+\subsection*{Data preparation}
 Countries were classified by World Bank country income group as upper middle (UM), lower middle (LM), and low (L) income.
@@
 
-\subsection{Statistical Analysis}
+\subsection*{Statistical analysis}
 We first summarised the key characteristics of studies and unique evaluations included in the review including distribution of CETs used and study conclusions.
@@
 
-\hspace{1em}
-
-\begin{table}[H]
-    \centering 
-    \caption{The facts about lorem ipsum generator from online sources.}
-    \begin{tabular}{|C{2cm}|L{10cm}|C{2.5cm}|}
-        \hline
-        \PlainInput{tables/char-included-studies}
-    \end{tabular}
-    \label{MyTable1}
-    \caption*{\footnotesize \textit{Notes:} Donec sit amet viverra justo. Duis malesuada velit}
-\end{table}
-
-\section{Results}
-\subsection{Study Sample and Selection}
+\section*{Results}
+\subsection*{Study sample and selection}
 The systematic search from databases returned 863 articles.
@@
 
-\subsection{Characteristics of Included Studies}
+\subsection*{Characteristics of included studies}
 Characteristics of the 57 included studies representing 196 evaluations are presented in Table 1.
@@
 
-\subsection{Descriptive results}
+\begin{table}[H]
+    \centering \singlespacing \small
+    \caption{Characteristics of included evaluations and unique studies}
+    \begin{tabular}{|L{6cm}|R{4.5cm}|R{4cm}|}
+        \hline
+        \PlainInput{tables/tab_evals_studies}
+    \end{tabular}
+    \label{tab_evals_studies}
+    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
+    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
+}
+\end{table}
+
+\begin{table}[H]
+    \centering \singlespacing \small
+    \caption{Characteristics of included evaluations and unique studies}
+    \begin{tabular}{|L{2.8cm}|C{1.8cm}|C{1.3cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|C{1cm}|}
+        \hline
+        \PlainInput{tables/tab_evals_thresholds}
+    \end{tabular}
+    \label{tab_evals_thresholds}
+    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
+    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
+}
+\end{table}
+
+\subsection*{Descriptive results}
 [In progress]
@@
     \centering
-    \includegraphics[width=1\linewidth]{output/figures/dose-price-income.png}
-    \caption{The facts about lorem ipsum generator from online sources.}
-    \label{fig:enter-label}
-    \caption*{\footnotesize \textit{Notes:} Lorem ipsum dolor sit amet}
+    \includegraphics[width=1\linewidth]{output/figures/prisma-flow-diagram.jpg}
+    \caption{PRISMA flow diagram.}
+    \label{fig:prisma-flow-diagram}
+    \caption*{\footnotesize \textit{}}
 \end{figure}
 
-\subsection{Factors associated with switching from cost-effective to not cost-effective}
+\subsection*{Factors associated with switching from cost-effective to not cost-effective}
 [In progress]
@@
 
-\subsection{Sensitivity Analyses}
+\subsection*{Sensitivity analyses}
 [In progress]
 
-\section{Discussion}
-\subsection{Interpretation of Results}
+\section*{Discussion}
+\subsection*{Interpretation of results}
 [In progress]
 
-\subsection{Strengths and Limitation}
+\subsection*{Strengths and limitation}
 Multi-country studies.66-69 why don't they report at country-level – this would be useful !

### 2024-06-30 output/tables/tab_likely_switch.tex
Updated

Characteristic & Threshold & Most likely switch\\
\hline
Type of comparison & Ochalek (2018) high & PCV7 vs NoVax (35.0\%, p=0.665)\\
\hline
Type of comparison & Ochalek (2018) low & PCV10 vs NoVax (48.4\%, p=0.514)\\
\hline
Type of comparison & Woods (2016) high & PCV10 vs NoVax (35.9\%, p=0.562)\\
\hline
Type of comparison & Woods (2016) low & PCV10 vs NoVax (78.1\%, p=0.043)\\
\hline
Type of comparison & P-Rivière (2023) high & PCV13 vs NoVax (26.5\%, p=0.961)\\
\hline
Type of comparison & P-Rivière (2023) low & PCV10 vs NoVax (53.1\%, p=0.764)\\
\hline
Income group & Ochalek (2018) high & Low (57.1\%, p=0.031)\\
\hline
Income group & Ochalek (2018) low & Low (57.1\%, p=0.122)\\
\hline
Income group & Woods (2016) high & Low (57.1\%, p=0.021)\\
\hline
Income group & Woods (2016) low & Lower-middle (85.7\%, p=0.056)\\
\hline
Income group & P-Rivière (2023) high & Low (57.1\%, p=0.003)\\
\hline
Income group & P-Rivière (2023) low & Lower-middle (60.7\%, p=0.240)\\
\hline
Herd effects & Ochalek (2018) high & Excluded (32.7\%, p=0.544)\\
\hline
Herd effects & Ochalek (2018) low & Excluded (43.0\%, p=0.706)\\
\hline
Herd effects & Woods (2016) high & Excluded (31.8\%, p=1.000)\\
\hline
Herd effects & Woods (2016) low & Excluded (72.9\%, p=0.155)\\
\hline
Herd effects & P-Rivière (2023) high & Excluded (24.3\%, p=1.000)\\
\hline
Herd effects & P-Rivière (2023) low & Excluded (51.4\%, p=0.350)\\
\hline
Serotype replacement & Ochalek (2018) high & Included (52.9\%, p=0.050)\\
\hline
Serotype replacement & Ochalek (2018) low & Included (52.9\%, p=0.433)\\
\hline
Serotype replacement & Woods (2016) high & Included (41.2\%, p=0.409)\\
\hline
Serotype replacement & Woods (2016) low & Included (82.4\%, p=0.271)\\
\hline
Serotype replacement & P-Rivière (2023) high & Included (41.2\%, p=0.126)\\
\hline
Serotype replacement & P-Rivière (2023) low & Excluded (48.8\%, p=1.000)\\
\hline
Study perspective & Ochalek (2018) high & Healthcare/payer (31.0\%, p=1.000)\\
\hline
Study perspective & Ochalek (2018) low & Healthcare/payer (44.0\%, p=0.611)\\
\hline
Study perspective & Woods (2016) high & Healthcare/payer (33.3\%, p=0.595)\\
\hline
Study perspective & Woods (2016) low & Societal (71.0\%, p=0.720)\\
\hline
Study perspective & P-Rivière (2023) high & Societal (25.8\%, p=0.698)\\
\hline
Study perspective & P-Rivière (2023) low & Healthcare/payer (51.2\%, p=0.506)\\
\hline

### 2024-07-03 code/analysis.R
Updated

@@ -1,300 +1,268 @@
+rm(list=ls())
+
+library(gt)
+library(gtsummary)
+library(tidyverse)
+library(scales)
+library(kableExtra)
+
 # Import studies from folder
 studies <- read.csv("data/studies.csv", row.names=NULL, stringsAsFactors=TRUE)
 
+Include = c("comparison", "doseNum", "perspective", "income", "herdEffects", 
+            "seroReplace", "efficacyPneum", "efficacyIPD", "efficacyOtitis", 
+            "budgetImpact", "studyDecide")
+Label   = list(comparison     = "Type of comparison",
+               doseNum        = "Number of doses",
+               perspective    = "Study perspective", 
+               income         = "Income group",
+               herdEffects    = "Included herd effects",
+               seroReplace    = "Included serotype replacement",
+               efficacyPneum  = "Pneumonia efficacy endpoint",
+               efficacyIPD    = "IPD efficacy endpoint",
+               efficacyOtitis = "Otitis media efficacy endpoint",
+               budgetImpact   = "Included budget impact analysis",
+               studyDecide    = "Study decision")
+
+comparisonLevels <- c("PCV7 vs NoVax", "PCV10 vs NoVax", "PCV13 vs NoVax", 
+                      "PCV13 vs PCV10", "Others")
+
+# Function to get type of comparison by unique studyid
+unique <- function(var) {
+  (studies %>% group_by(across(var)) %>% 
+     summarise(n = n_distinct(across(studyID))))$n
+}
+
+studies <- studies %>% 
+  mutate(comparison = factor(comparison, levels=comparisonLevels),
+         doseNum = factor(doseNum, levels=c("Four", "Three", "One/two", "Unknown")),
+         studyDecide = factor(studyDecide, levels=c("Cost-saving", "Cost-effective",
+                                                    "Not cost-effective")))
+
+# Table of study characteristics 
+df1 <- studies %>%
+  tbl_summary(missing="no",  include=all_of(Include), label=Label,
+              digits    = everything() ~ c(0,0))  %>% 
+  modify_header(stat_0 ~ "Number (%) of evaluations, N={n}")
+
+df2 <- studies %>%
+  tbl_summary(missing="no",  include=all_of(Include), label=Label,
[…]

### 2024-07-14 code/analysis.R
Update analysis.R

@@ -114,6 +114,10 @@ studies <- studies %>%
                                   TRUE ~ switches),
          anySwitch = case_when(is.na(new_switches) ~ NA, 
                                new_switches!=0 ~ 1,
+                               TRUE ~ 0),
+         # Natalie analysis
+         anySwitch2 = case_when(is.na(new_switches) ~ 1, 
+                               new_switches!=0 ~ 1,
                                TRUE ~ 0))
 
 
@@ -262,7 +266,61 @@ t.test(priceIntvUSD ~ switchRL, studies)
 
 
 ttest <- t.test(priceIntvUSD ~ anySwitch, studies)
+
 ttest$estimate
 ttest$conf.int
 ttest$p.value
+
+# Exclude rows with missing values in 'anySwitch' before calculating weights
+df_filtered <- studies %>% 
+  filter(!is.na(anySwitch)) %>% 
+  group_by(studyID) %>%
+  mutate(weights = 1/n()) %>% 
+  select(studyID, uniqueID, weights)
+
+# Merge the weights back to the original data frame, setting weight to 0 for excluded rows
+studies <- studies %>%
+  left_join(df_filtered, by = "uniqueID") %>%
+  mutate(weights = ifelse(is.na(weights), 0, weights)) %>% 
+  select(-studyID.y)
+
+# Create new data frame, no rows with missing price and other comparisons
+df_model <- studies %>%
+  filter(!is.na(priceIntvUSD), comparison!="Others")
+
+
+# Replicating original (NC) analysis
+print(summary(glm(anySwitch2 ~ comparison + perspective + income + 
+                herdEffects + seroReplace + priceIntvUSD,
+              family = binomial(link = "probit"), data = df_model)),
+        digits = 1)
+
+# Fit a probit model on anySwitch with weights
+model <- studies %>%
+  filter(!is.na(anySwitch), comparison != "Others")
+
+glm(anySwitch2 ~ comparison + perspective + income + 
+      herdEffects + seroReplace + priceIntvUSD,
+    family = binomial(link = "probit"), data = model2)
+
+
+probit <- glm(anySwitch ~ comparison + perspective + income + 
+                herdEffects + seroReplace + priceIntvUSD,
+              family = binomial(link = "probit"), data = df_model)
+print(summary(probit), digits = 1)
+tbl_regression(probit, exponentiate = F)
+
+probitW <- glm(anySwitch ~ comparison + perspective + income + 
+                 herdEffects + seroReplace + priceIntvUSD,
[…]

### 2024-07-14 manuscript.tex
Updates from Overleaf

--- 2024-06-30 output/manuscript.tex
@@
 \documentclass[12pt]{article}
-
-\usepackage{latex/ediArticle}  %from ediArticle.sty
-\usepackage{amsmath}
-
-% Settings for the author block
-\usepackage{authblk}
-\usepackage{ragged2e}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% left align title, authors, and affiliations
-\makeatletter
-\renewcommand\maketitle{\par
-  \begingroup
-    \flushleft
-    \LARGE \setstretch{1.1} {\@title}\par
-  \endgroup
-  \vspace{-0.2em}
-  \begin{flushleft}
-    \large \setstretch{1.1} \@author
-  \end{flushleft}
-}
-\makeatother
-\renewcommand\Affilfont{\small \itshape}
+\usepackage{assets/main}  %from manuscript.sty
 
@@
 \begin{document}
+\fontsize{13pt}{15pt}\selectfont % Font size 13pt
+\maketitle
 
-% Set font size to 13pt
-\fontsize{13pt}{15pt}\selectfont
-
-\maketitle
 \textit{Funding/support:}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Abstract}
+\section{Abstract}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Highlights}
+\section{Highlights}
 Authors should identify 2–3 "Highlights" that illustrate the paper's contribution to the field. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Introduction}
+\section{Introduction}
+The use of  pneumococcal conjugate vaccines (PCVs) has  reduced the burden of pneumonia, one of the leading cause of deaths in children under five years globally [REF].
+In 20XX, the prevalence was YYY.
+PCVs are recommended by WHO but are costly compared to most childhood vaccines.
+Introduction and coverage of these vaccines have therefore been high in high income countries and, through Gavi/AMC support, many low middle income countries.
+[???trend in roll out over time].
+but lagging in middle-income countries or those lacking Gavi/AMC eligibility.
+PCV introduction is guided by health technology assessment (HTA) processes in many LMICs.
+Ex Thailand, Philippines, China.
+In other settings ex Pacific islands and sub-Saharah African countries, no HTA processes exist, and PCV programs are introduced based on donor or development partner support [REF].
 
-[Not started – outline only below]
--	Pneumococcal disease burden globally (and trend over time), 
--	Availability of effective and safe vaccines; PCVs recommended by WHO; But costly compared to most childhood vaccines 
--	Introduction/coverage of these vaccines: High use in high income and many low-income countries… trend in roll out over time. Lagging middle-income countries, those lacking Gavi/AMC eligibility.
--	PCV  introduction guided by HTA processes in many LMICs.
-Ex Thailand, Philippines, China.
-In other settings ex Pacific islands, no HTA processes available – based on donor or development partner support
-
--	One component of HTA is cost-effectiveness analysis: CEA is method for weighing costs and outcomes in comparable method across interventions – provides guidance on value for money of new technologies.
+One component of HTA process is cost-effectiveness analysis (CEA).
+CEA is method for weighing costs and outcomes in comparable method across interventions and thus provides guidance on value for money of new technologies.
 Results are typically presented as incremental cost-effectiveness ratios, in \$/QALY gained or \$/DALY averted.
 If a vaccine is found to be cost-saving, usually implemented pending other factors (budget impact, political and equity considerations, and other practical and logistical considerations including availability of vaccine, etc).
-Vaccines that are not cost-saving, but result in higher costs and higher health benefits, are often compared to country-specific willingness to pay thresholds, to determine whether an intervention is considered cost-effective, or good value for money.
+Vaccines that are not cost-saving, but result in higher costs and higher health benefits, are often compared to country-specific willingness to pay thresholds, to determine whether an intervention is considered cost-effective (that is, of good value for money).
+Recent systematic reviews PCV is CE across (most)( LMICs (sometimes cost-saving) \supercite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}.
+Cost-effectiveness is influenced by vaccine price (local acquisition), inclusion/exclusion of indirect effects (serotype replacement and herd effects), cross protection, disease burden (Incidence / mortality from invasive pneumococcal disease (IPD), and pneumonia), and vaccine efficacy and coverage
 
--	Recent systematic reviews1-4 PCV is CE across (most)( LMICs (sometimes cost-saving).
-Cost-effectiveness is influenced by vaccine price (local acquisition), inclusion/exclusion of indirect effects (serotype replacement and herd effects), cross protection, disease burden (Incidence / mortality from IPD and pneumonia), and vaccine efficacy and coverage
--	Where are we at with willingness to pay thresholds in LMICs?
-Historically thresholds of 1-3 x gross domestic product (GDP) per capita have been used to assess the cost-effectiveness of vaccines and other interventions in low- and middle-income countries .
-Others thresholds have existed but unclear the origins of these, and what they are based on.
-
-Newer  country-specific estimates 2-3 of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
-New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
-Several countries are in process of developing these thresholds (ex: Indonesia ).
-New estimates from \textcite{woods_country-level_2016} (based on 1 empirical estimate from a high-income setting), \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs), and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
-\textcite{woods_country-level_2016} also provides these estimates for high-income countries.
-
--	Despite the World Health Organization and others recommending against using GDP per capita-based thresholds for judging the value for money of healthcare interventions most recent studies continue to do so4.
+Historically thresholds of 1-3 x gross domestic product (GDP) per capita have been used to assess the cost-effectiveness of vaccines and other interventions in low- and middle-income countries.
+They were proposed by the World Health Organization (WHO) Commission on Macroeconomics and Health (CMH) based on human capital considerations rather than health opportunity costs [REF].
+Hence, they represented what the CMH believed governments should pay for improved health, rather than what interventions to choose given a fixed healthcare budget.
+They became widely cited and used to evaluate individual interventions, but WHO produced a paper advising against the use of GDP-based thresholds, especially in isolation from other considerations \parencite{bertram_costeffectiveness_2016}.
+Despite the World Health Organization and others recommending against using GDP per capita-based thresholds for judging the value for money of healthcare interventions most recent studies continue to do so4.
 Recent systematic review of 230 studies (713 interventions) published CEAs in LMICs: 1-3 × GDP/ capita was the most common type of threshold used (84.3\%) ; ~ A third of studies (34.2\%) using 1 to 3× GDP per capita applied a threshold at 3× GDP per capita.
@@
 79.3\% of interventions received a recommendation as “cost-effective”.
--	What do new(er) thresholds mean for previously published CEAs?
 
-The aim of this study is to investigate whether new country-specific estimates on cost-effectiveness thresholds (CET) based on health opportunity costs may impact on study conclusions about the cost-effectiveness of pneumococcal conjugate vaccine programs in low- and middle-income countries.
+Newer country-specific estimates of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
+\supercite{ochalek_estimating_2018, pichon-riviere_determining_2023,woods_country-level_2016} New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
+Several countries are in process of developing these thresholds (ex: Indonesia ).
+New estimates from \textcite{woods_country-level_2016} (based on one empirical estimate from a high-income setting), \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs), and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
+\textcite{woods_country-level_2016} also provides these estimates for high-income countries.
+The main aim of this study is to investigate whether these estimates on cost-effectiveness thresholds (CET) based on health opportunity costs may impact on study conclusions about the cost-effectiveness of pneumococcal conjugate vaccine programs in low- and middle-income countries.
 A secondary aim is to investigate which study factors are influential in driving study conclusions that switch from finding PCV to be cost-effective to not cost-effective.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Methods}
-\subsection*{Systematic search}
+\section{Methods}
+\subsection{Systematic search}
 We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.\supercite{saokaew_cost_2016} We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-benefit OR cost-utility OR cost-effectiveness OR cost-benefit OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 25 April 2022.
 The search was limited to low- and middle-income countries (LMICs) using country names and related LMIC terminology (see Appendix 1 in Supplementary Material).
-We also checked published systematic reviews on economic evaluation of PCV for additional studies.1-4
+We also checked published systematic reviews on economic evaluation of PCV for additional studies.\supercite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}
 
@@
 
-\subsection*{Data preparation}
+\subsection{Data preparation}
 Countries were classified by World Bank country income group as upper middle (UM), lower middle (LM), and low (L) income.
@@
 
-\subsection*{Statistical analysis}
+\subsection{Statistical analysis}
 We first summarised the key characteristics of studies and unique evaluations included in the review including distribution of CETs used and study conclusions.
@@
 
-Analyses were performed using Microsoft Excel (Microsoft Corporation, 2023) and Stata version 17.0 SE (StataCorp 2021).
+Analyses were performed using R version 4.4.1 (R Foundation for Statistical Computing, Vienna, Austria).
 
-\section*{Results}
-\subsection*{Study sample and selection}
+\section{Results}
+\subsection{Study sample and selection}
 The systematic search from databases returned 863 articles.
@@
 
-\subsection*{Characteristics of included studies}
+\subsection{Characteristics of included studies}
 Characteristics of the 57 included studies representing 196 evaluations are presented in Table 1.
@@
     \caption{Characteristics of included evaluations and unique studies}
-    \begin{tabular}{|L{6cm}|R{4.5cm}|R{4cm}|}
+    \begin{tabular}{|L{6cm}|C{4.5cm}|C{4cm}|}
         \hline
@@
     \label{tab_evals_thresholds}
-    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
-    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
+    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7.
+IPD, invasive pneumococcal disease; NoVax, no vaccination; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV.
 }
@@
 
-\subsection*{Descriptive results}
+\subsection{Descriptive results}
 [In progress]
@@
     \centering
-    \includegraphics[width=1\linewidth]{output/figures/prisma-flow-diagram.jpg}
+    \includegraphics[width=1\linewidth]{figures/prisma-flow-diagram.jpg}
     \caption{PRISMA flow diagram.}
@@
 
-\subsection*{Factors associated with switching from cost-effective to not cost-effective}
+\subsection{Factors associated with switching from cost-effective to not cost-effective}
 [In progress]
@@
 
-\subsection*{Sensitivity analyses}
+\begin{table}[H]
+    \centering \singlespacing \small
+    \caption{Characteristics of included evaluations and unique studies}
+    \begin{tabular}{|L{4.5cm}|L{4cm}|C{2.75cm}|C{2.75cm}|}
+        \hline
+        \PlainInput{tables/tab_likely_anyswitch}
+    \end{tabular}
+    \label{tab_likely_anyswitch}
+    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
+    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
+}
+\end{table}
+
+\subsection{Sensitivity analyses}
 [In progress]
 
-\section*{Discussion}
-\subsection*{Interpretation of results}
+\section{Discussion}
+\subsection{Interpretation of results}
 [In progress]
 
-\subsection*{Strengths and limitation}
+\subsection{Strengths and limitation}
 Multi-country studies.66-69 why don't they report at country-level – this would be useful !

### 2024-07-14 supplement.tex
Updates from Overleaf

\documentclass[12pt]{article}
\usepackage{latex/supp}  %from ediArticle.sty

\title{\textbf{Supplementary Appendix} \\
Reassessing the cost-effectiveness of pneumococcal conjugate vaccines in low- and middle-income countries using opportunity cost-based thresholds}
\author[1,*]{Natalie Carvalho, PhD}
\author[1,2]{Edifofon Akpan, MPH}
\author[3,4]{Fiona Russell, PhD}
\author[5]{Mark Jit, PhD}
\affil[1]{Centre for Health Policy, Melbourne School of Population and Global Health, The University of Melbourne, Australia.}
\affil[2]{Sheffield Centre for Health and Related Research, School of Medicine and Population Health, The University of Sheffield, United Kingdom.}
\affil[3]{Department of Infection and Immunity, Murdoch Children's Research Institute, Royal Children's Hospital, Australia.}
\affil[4]{Department of Paediatrics, The University of Melbourne, Australia.}
\affil[5]{Department of Infectious Disease Epidemiology, Faculty of Epidemiology and Population Health, London School of Hygiene and Tropical Medicine, United Kingdom.}
\affil[*]{Corresponding author: natalie.carvalho@unimelb.edu.au; +613 8344 3715}

\date{}

\begin{document}

\fontsize{10pt}{12pt}\selectfont % Font size 10pt

\maketitle

\clearpage

\section{Search strings for databases}
\subsection{Scopus - 217}
( TITLE-ABS-KEY ( pneumococc* ) AND TITLE-ABS-KEY ( conjugat* ) AND TITLE-ABS-KEY ( vaccin* OR immun* ) AND TITLE-ABS-KEY ( economic OR cost-effectiveness OR cost-utility ) AND TITLE-ABS-KEY ( afghanistan OR albania OR algeria OR "American Samoa" OR angola OR argentina OR "Argentine Republic" OR armenia OR azerbaijan OR bangladesh OR belarus OR byelarus OR belorussia OR belize OR benin OR bhutan OR bolivia OR bosnia OR botswana OR brazil OR bulgaria OR burma OR "Burkina Faso" OR burundi OR "Cabo Verde" OR "Cape verde" OR cambodia OR cameroon OR "Central African Republic" OR chad OR china OR colombia OR comoros OR comores OR comoro OR congo OR "Costa Rica" OR "Côte d'Ivoire" OR cuba OR djibouti OR dominica OR "Dominican Republic" OR ecuador OR egypt OR "El Salvador" OR eritrea OR ethiopia OR fiji OR gabon OR gambia OR gaza OR "Georgia Republic" OR georgian OR ghana OR grenada OR grenadines OR guatemala OR guinea OR "Guinea Bissau" OR guyana OR haiti OR herzegovina OR hercegovina OR honduras OR india OR indonesia OR iran OR iraq OR jamaica OR jordan OR kazakhstan OR kenya OR kiribati OR korea OR kosovo OR kyrgyz OR kirghizia OR kirghiz OR kirgizstan OR kyrgyzstan OR "Lao PDR" OR laos OR lebanon OR lesotho OR liberia OR libya OR macedonia OR madagascar OR malawi OR malay OR malaya OR malaysia OR maldives OR mali OR "Marshall Islands" OR mauritania OR mauritius OR mexico OR micronesia OR moldova OR mongolia OR montenegro OR morocco OR mozambique OR myanmar OR namibia OR nauru OR nepal OR nicaragua OR niger OR nigeria OR pakistan OR palau OR panama OR "Papua New Guinea" OR paraguay OR peru OR philippines OR phillippines OR philipines OR phillipines OR principe OR romania OR rwanda OR ruanda OR samoa OR "Sao Tome" OR senegal OR serbia OR "Sierra Leone" OR "Solomon Islands" OR somalia OR "South Africa" OR "South Sudan" OR "Sri Lanka" OR "St Lucia" OR "St Vincent" OR sudan OR surinam OR suriname OR swaziland OR syria OR "Syrian Arab Republic" OR tajikistan OR tadzhikistan OR tadjikistan OR tadzhik OR tanzania OR thailand OR timor OR togo OR tonga OR tunisia OR turkey OR turkmen OR turkmenistan OR tuvalu OR uganda OR ukraine OR uzbek OR uzbekistan OR vanuatu OR venezuela OR vietnam OR "West Bank" OR yemen OR zambia OR zimbabwe OR "developing country" OR "developing countries" OR "developing nation" OR "developing nations" OR "developing population" OR "developing populations" OR "developing world" OR "less developed country" OR "less developed countries" OR "less developed nation" OR "less developed nations" OR "less developed population" OR "less developed populations" OR "less developed world" OR "lesser developed country" OR "lesser developed countries" OR "lesser developed nation" OR "lesser developed nations" OR "lesser developed population" OR "lesser developed populations" OR "lesser developed world" OR "under developed country" OR "under developed countries" OR "under developed nation" OR "under developed nations" OR "under developed population" OR "under developed populations" OR "under developed world" OR "underdeveloped country" OR "underdeveloped countries" OR "underdeveloped nation" OR "underdeveloped nations" OR "underdeveloped population" OR "underdeveloped populations" OR "underdeveloped world" OR "middle income country" OR "middle income countries" OR "middle income nation" OR "middle income nations" OR "middle income population" OR "middle income populations" OR "low income country" OR "low income countries" OR "low income nation" OR "low income nations" OR "low income population" OR "low income populations" OR "lower income country" OR "lower income countries" OR "lower income nation" OR "lower income nations" OR "lower income population" OR "lower income populations" OR "underserved country" OR "underserved countries" OR "underserved nation" OR "underserved nations" OR "underserved population" OR "underserved populations" OR "underserved world" OR "under served country" OR "under served countries" OR "under served nation" OR "under served nations" OR "under served population" OR "under served populations" OR "under served world" OR "deprived country" OR "deprived countries" OR "deprived nation" OR "deprived nations" OR "deprived population" OR "deprived populations" OR "deprived world" OR "poor country" OR "poor countries" OR "poor nation" OR "poor nations" OR "poor population" OR "poor populations" OR "poor world" OR "poorer country" OR "poorer countries" OR "poorer nation" OR "poorer nations" OR "poorer population" OR "poorer populations" OR "poorer world" OR "developing economy" OR "developing economies" OR "less developed economy" OR "less developed economies" OR "lesser developed economy" OR "lesser developed economies" OR "under developed economy" OR "under developed economies" OR "underdeveloped economy" OR "underdeveloped economies" OR "middle income economy" OR "middle income economies" OR "low income economy" OR "low income economies" OR "lower income economy" OR "lower income economies" OR "low gdp" OR "low gnp" OR "low gross domestic" OR "low gross national" OR "lower gdp" OR "lower gnp" OR "lower gross domestic" OR "lower gross national" OR lmic OR lmics OR "third world" OR "lami country" OR "lami countries" OR "transitional country" OR "transitional countries" ) )

\subsection{Web of Science - 256}
((((TS=(pneumococc* )) AND TS=(conjugat*)) AND TS=(vaccin* OR immun*)) AND TS=(economic OR cost-effectiveness OR cost-utility)) AND TS=(afghanistan OR albania OR algeria OR "American Samoa" OR angola OR argentina OR "Argentine Republic" OR armenia OR azerbaijan OR bangladesh OR belarus OR byelarus OR belorussia OR belize OR benin OR bhutan OR bolivia OR bosnia OR botswana OR brazil OR bulgaria OR burma OR "Burkina Faso" OR burundi OR "Cabo Verde" OR "Cape verde" OR cambodia OR cameroon OR "Central African Republic" OR chad OR china OR colombia OR comoros OR comores OR comoro OR congo OR "Costa Rica" OR "Côte d'Ivoire" OR cuba OR djibouti OR dominica OR "Dominican Republic" OR ecuador OR egypt OR "El Salvador" OR eritrea OR ethiopia OR fiji OR gabon OR gambia OR gaza OR "Georgia Republic" OR georgian OR ghana OR grenada OR grenadines OR guatemala OR guinea OR "Guinea Bissau" OR guyana OR haiti OR herzegovina OR hercegovina OR honduras OR india OR indonesia OR iran OR iraq OR jamaica OR jordan OR kazakhstan OR kenya OR kiribati OR korea OR kosovo OR kyrgyz OR kirghizia OR kirghiz OR kirghizstan OR kyrgyzstan OR "Lao PDR" OR laos OR lebanon OR lesotho OR liberia OR libya OR macedonia OR madagascar OR malawi OR malay OR malaya OR malaysia OR maldives OR mali OR "Marshall Islands" OR mauritania OR mauritius OR mexico OR micronesia OR moldova OR mongolia OR montenegro OR morocco OR mozambique OR myanmar OR namibia OR nauru OR nepal OR nicaragua OR niger OR nigeria OR pakistan OR palau OR panama OR "Papua New Guinea" OR paraguay OR peru OR philippines OR philippines OR philippines OR phillippines OR principe OR romania OR rwanda OR ruanda OR samoa OR "Sao Tome" OR senegal OR serbia OR "Sierra Leone" OR "Solomon Islands" OR somalia OR "South Africa" OR "South Sudan" OR "Sri Lanka" OR "St Lucia" OR "St Vincent" OR sudan OR surinam OR suriname OR swaziland OR syria OR "Syrian Arab Republic" OR tajikistan OR tadzhikistan OR tadjikistan OR tadzhika OR tanzania OR thailand OR timor OR togo OR tonga OR tunisia OR turkey OR turkmen OR turkmenistan OR tuvalu OR uganda OR ukraine OR uzbek OR uzbekistan OR vanuatu OR venezuela OR vietnam OR "West Bank" OR yemen OR zambia OR zimbabwe OR "developing country" OR "developing countries" OR "developing nation" OR "developing nations" OR "developing population" OR "developing populations" OR "developing world" OR "less developed country" OR "less developed countries" OR "less developed nation" OR "less developed nations" OR "less developed population" OR "less developed populations" OR "less developed world" OR "lesser developed country" OR "lesser developed countries" OR "lesser developed nation" OR "lesser developed nations" OR "lesser developed population" OR "lesser developed populations" OR "lesser developed world" OR "under developed country" OR "under developed countries" OR "under developed nation" OR "under developed nations" OR "under developed population" OR "under developed populations" OR "under developed world" OR "underdeveloped country" OR "underdeveloped countries" OR "underdeveloped nation" OR "underdeveloped nations" OR "underdeveloped population" OR "underdeveloped populations" OR "underdeveloped world" OR "middle income country" OR "middle income countries" OR "middle income nation" OR "middle income nations" OR "middle income population" OR "middle income populations" OR "low income country" OR "low income countries" OR "low income nation" OR "low income nations" OR "low income population" OR "low income populations" OR "lower income country" OR "lower income countries" OR "lower income nation" OR "lower income nations" OR "lower income population" OR "lower income populations" OR "underserved country" OR "underserved countries" OR "underserved nation" OR "underserved nations" OR "underserved population" OR "underserved populations" OR "underserved world" OR "under served country" OR "under served countries" OR "under served nation" OR "under served nations" OR "under served population" OR "under served populations" OR "under served world" OR "deprived country" OR "deprived countries" OR "deprived nation" OR "deprived nations" OR "deprived population" OR "deprived populations" OR "deprived world" OR "poor country" OR "poor countries" OR "poor nation" OR "poor nations" OR "poor population" OR "poor populations" OR "poor world" OR "poorer country" OR "poorer countries" OR "poorer nation" OR "poorer nations" OR "poorer population" OR "poorer populations" OR "poorer world" OR "developing economy" OR "developing economies" OR "less developed economy" OR "less developed economies" OR "lesser developed economy" OR "lesser developed economies" OR "under developed economy" OR "under developed economies" OR "underdeveloped economy" OR "underdeveloped economies" OR "middle income economy" OR "middle income economies" OR "low income economy" OR "low income economies" OR "lower income economy" OR "lower income economies" OR "low gdp" OR "low gnp" OR "low gross domestic" OR "low gross national" OR "lower gdp" OR "lower gnp" OR "lower gross domestic" OR "lower gross national" OR lmic OR lmics OR "third world" OR "lami country" OR "lami countries" OR "transitional country" OR "transitional countries" )

\subsection{PubMed - 165}
((((pneumococc*[tw]) AND (conjugat*[tw])) AND (vaccin*[tw] OR immun*[tw])) AND (economic[tw] OR cost-effectiveness[tw] OR cost-utility[tw])) AND (Afghanistan[tw] OR Albania[tw] OR Algeria[tw] OR "American Samoa"[tw] OR Angola[tw] OR Argentina[tw] OR "Argentine Republic"[tw] OR Armenia[tw] OR Azerbaijan[tw] OR Bangladesh[tw] OR Belarus[tw] OR Byelarus[tw] OR Belorussia[tw] OR Belize[tw] OR Benin[tw] OR Bhutan[tw] OR Bolivia[tw] OR Bosnia[tw] OR Botswana[tw] OR Brazil[tw] OR Bulgaria[tw] OR Burma[tw] OR "Burkina Faso"[tw] OR Burundi[tw] OR "Cabo Verde"[tw] OR "Cape verde"[tw] OR Cambodia[tw] OR Cameroon[tw] OR "Central African Republic"[tw] OR Chad[tw] OR China[tw] OR Colombia[tw] OR Comoros[tw] OR Comores[tw] OR Comoro[tw] OR Congo[tw] OR "Costa Rica"[tw] OR "Côte d'Ivoire"[tw] OR Cuba[tw] OR Djibouti[tw] OR Dominica[tw] OR "Dominican Republic"[tw] OR Ecuador[tw] OR Egypt[tw] OR "El Salvador"[tw] OR Eritrea[tw] OR Ethiopia[tw] OR Fiji[tw] OR Gabon[tw] OR Gambia[tw] OR Gaza[tw] OR "Georgia Republic"[tw] OR Georgian[tw] OR Ghana[tw] OR Grenada[tw] OR Grenadines[tw] OR Guatemala[tw] OR Guinea[tw] OR "Guinea Bissau"[tw] OR Guyana[tw] OR Haiti[tw] OR Herzegovina[tw] OR Hercegovina[tw] OR Honduras[tw] OR India[tw] OR Indonesia[tw] OR Iran[tw] OR Iraq[tw] OR Jamaica[tw] OR Jordan[tw] OR Kazakhstan[tw] OR Kenya[tw] OR Kiribati[tw] OR Korea[tw] OR Kosovo[tw] OR Kyrgyz[tw] OR Kirghizia[tw] OR Kirghiz[tw] OR Kirgizstan[tw] OR Kyrgyzstan[tw] OR "Lao PDR"[tw] OR Laos[tw] OR Lebanon[tw] OR Lesotho[tw] OR Liberia[tw] OR Libya[tw] OR Macedonia[tw] OR Madagascar[tw] OR Malawi[tw] OR Malay[tw] OR Malaya[tw] OR Malaysia[tw] OR Maldives[tw] OR Mali[tw] OR "Marshall Islands"[tw] OR Mauritania[tw] OR Mauritius[tw] OR Mexico[tw] OR Micronesia[tw] OR Moldova[tw] OR Mongolia[tw] OR Montenegro[tw] OR Morocco[tw] OR Mozambique[tw] OR Myanmar[tw] OR Namibia[tw] OR Nauru[tw] OR Nepal[tw] OR Nicaragua[tw] OR Niger[tw] OR Nigeria [tw] OR Pakistan [tw] OR Palau[tw] OR Panama[tw] OR "Papua New Guinea"[tw] OR Paraguay[tw] OR Peru [tw] OR Philippines[tw] OR Phillippines[tw] OR Philipines[tw] OR Phillipines[tw] OR Principe[tw] OR Romania[tw] OR Rwanda[tw] OR Ruanda[tw] OR Samoa[tw] OR "Sao Tome"[tw] OR Senegal[tw] OR Serbia[tw] OR "Sierra Leone"[tw] OR "Solomon Islands"[tw] OR Somalia[tw] OR "South Africa"[tw] OR "South Sudan"[tw] OR "Sri Lanka"[tw] OR "St Lucia"[tw] OR "St Vincent"[tw] OR Sudan[tw] OR Surinam[tw] OR Suriname[tw] OR Swaziland[tw] OR Syria[tw] OR "Syrian Arab Republic"[tw] OR Tajikistan[tw] OR Tadzhikistan[tw] OR Tadjikistan[tw] OR Tadzhik[tw] OR Tanzania[tw] OR Thailand[tw] OR Timor[tw] OR Togo[tw] OR Tonga[tw] OR Tunisia[tw] OR Turkey[tw] OR Turkmen[tw] OR Turkmenistan[tw] OR Tuvalu[tw] OR Uganda[tw] OR Ukraine[tw] OR Uzbek[tw] OR Uzbekistan[tw] OR Vanuatu[tw] OR Venezuela[tw] OR Vietnam[tw] OR "West Bank"[tw] OR Yemen[tw] OR Zambia[tw] OR Zimbabwe[tw] OR "developing country"[tw] OR "developing countries"[tw] OR "developing nation"[tw] OR "developing nations"[tw] OR "developing population"[tw] OR "developing populations"[tw] OR "developing world"[tw] OR "less developed country"[tw] OR "less developed countries"[tw] OR "less developed nation"[tw] OR "less developed nations"[tw] OR "less developed population"[tw] OR "less developed populations"[tw] OR "less developed world"[tw] OR "lesser developed country"[tw] OR "lesser developed countries"[tw] OR "lesser developed nation"[tw] OR "lesser developed nations"[tw] OR "lesser developed population"[tw] OR "lesser developed populations"[tw] OR "lesser developed world"[tw] OR "under developed country"[tw] OR "under developed countries"[tw] OR "under developed nation"[tw] OR "under developed nations"[tw] OR "under developed population"[tw] OR "under developed populations"[tw] OR "under developed world"[tw] OR "underdeveloped country"[tw] OR "underdeveloped countries"[tw] OR "underdeveloped nation"[tw] OR "underdeveloped nations"[tw] OR "underdeveloped population"[tw] OR "underdeveloped populations"[tw] OR "underdeveloped world"[tw] OR "middle income country"[tw] OR "middle income countries"[tw] OR "middle income nation"[tw] OR "middle income nations"[tw] OR "middle income population"[tw] OR "middle income populations"[tw] OR "low income country"[tw] OR "low income countries"[tw] OR "low income nation"[tw] OR "low income nations"[tw] OR "low income population"[tw] OR "low income populations"[tw] OR "lower income country"[tw] OR "lower income countries"[tw] OR "lower income nation"[tw] OR "lower income nations"[tw] OR "lower income population"[tw] OR "lower income populations"[tw] OR "underserved country"[tw] OR "underserved countries"[tw] OR "underserved nation"[tw] OR "underserved nations"[tw] OR "underserved population"[tw] OR "underserved populations"[tw] OR "underserved world"[tw] OR "under served country"[tw] OR "under served countries"[tw] OR "under served nation"[tw] OR "under served nations"[tw] OR "under served population"[tw] OR "under served populations"[tw] OR "under served world"[tw] OR "deprived country"[tw] OR "deprived countries"[tw] OR "deprived nation"[tw] OR "deprived nations"[tw] OR "deprived population"[tw] OR "deprived populations"[tw] OR "deprived world"[tw] OR "poor country"[tw] OR "poor countries"[tw] OR "poor nation"[tw] OR "poor nations"[tw] OR "poor population"[tw] OR "poor populations"[tw] OR "poor world"[tw] OR "poorer country"[tw] OR "poorer countries"[tw] OR "poorer nation"[tw] OR "poorer nations"[tw] OR "poorer population"[tw] OR "poorer populations"[tw] OR "poorer world"[tw] OR "developing economy"[tw] OR "developing economies"[tw] OR "less developed economy"[tw] OR "less developed economies"[tw] OR "lesser developed economy"[tw] OR "lesser developed economies"[tw] OR "under developed economy"[tw] OR "under developed economies"[tw] OR "underdeveloped economy"[tw] OR "underdeveloped economies"[tw] OR "middle income economy"[tw] OR "middle income economies"[tw] OR "low income economy"[tw] OR "low income economies"[tw] OR "lower income economy"[tw] OR "lower income economies"[tw] OR "low gdp"[tw] OR "low gnp"[tw] OR "low gross domestic"[tw] OR "low gross national"[tw] OR "lower gdp"[tw] OR "lower gnp"[tw] OR "lower gross domestic"[tw] OR "lower gross national"[tw] OR lmic OR lmics OR "third world"[tw] OR "lami country"[tw] OR "lami countries"[tw] OR "transitional country"[tw] OR "transitional countries"[tw])

\subsection{EMBASE (Ovid) - 225}
(pneumococc* and conjugat* and (vaccin* or immun*) and (economic or cost-effectiveness or cost-utility) and (afghanistan or albania or algeria or "American Samoa" or angola or argentina or "Argentine Republic" or armenia or azerbaijan or bangladesh or belarus or byelarus or belorussia or belize or benin or bhutan or bolivia or bosnia or botswana or brazil or bulgaria or burma or "Burkina Faso" or burundi or "Cabo Verde" or "Cape verde" or cambodia or cameroon or "Central African Republic" or chad or china or colombia or comoros or comores or comoro or congo or "Costa Rica" or "Côte d'Ivoire" or cuba or djibouti or dominica or "Dominican Republic" or ecuador or egypt or "El Salvador" or eritrea or ethiopia or fiji or gabon or gambia or gaza or "Georgia Republic" or georgian or ghana or grenada or grenadines or guatemala or guinea or "Guinea Bissau" or guyana or haiti or herzegovina or hercegovina or honduras or india or indonesia or iran or iraq or jamaica or jordan or kazakhstan or kenya or kiribati or korea or kosovo or kyrgyz or kirghizia or kirghiz or kirghizstan or kyrgyzstan or "Lao PDR" or laos or lebanon or lesotho or liberia or libya or macedonia or madagascar or malawi or malay or malaya or malaysia or maldives or mali or "Marshall Islands" or mauritania or mauritius or mexico or micronesia or moldova or mongolia or montenegro or morocco or mozambique or myanmar or namibia or nauru or nepal or nicaragua or niger or nigeria or pakistan or palau or panama or "Papua New Guinea" or paraguay or peru or philippines or philippines or philippines or phillippines or principe or romania or rwanda or ruanda or samoa or "Sao Tome" or senegal or serbia or "Sierra Leone" or "Solomon Islands" or somalia or "South Africa" or "South Sudan" or "Sri Lanka" or "St Lucia" or "St Vincent" or sudan or surinam or suriname or swaziland or syria or "Syrian Arab Republic" or tajikistan or tadzhikistan or tadjikistan or tadzhika or tanzania or thailand or timor or togo or tonga or tunisia or turkey or turkmen or turkmenistan or tuvalu or uganda or ukraine or uzbek or uzbekistan or vanuatu or venezuela or vietnam or "West Bank" or yemen or zambia or zimbabwe or "developing country" or "developing countries" or "developing nation" or "developing nations" or "developing population" or "developing populations" or "developing world" or "less developed country" or "less developed countries" or "less developed nation" or "less developed nations" or "less developed population" or "less developed populations" or "less developed world" or "lesser developed country" or "lesser developed countries" or "lesser developed nation" or "lesser developed nations" or "lesser developed population" or "lesser developed populations" or "lesser developed world" or "under developed country" or "under developed countries" or "under developed nation" or "under developed nations" or "under developed population" or "under developed populations" or "under developed world" or "underdeveloped country" or "underdeveloped countries" or "underdeveloped nation" or "underdeveloped nations" or "underdeveloped population" or "underdeveloped populations" or "underdeveloped world" or "middle income country" or "middle income countries" or "middle income nation" or "middle income nations" or "middle income population" or "middle income populations" or "low income country" or "low income countries" or "low income nation" or "low income nations" or "low income population" or "low income populations" or "lower income country" or "lower income countries" or "lower income nation" or "lower income nations" or "lower income population" or "lower income populations" or "underserved country" or "underserved countries" or "underserved nation" or "underserved nations" or "underserved population" or "underserved populations" or "underserved world" or "under served country" or "under served countries" or "under served nation" or "under served nations" or "under served population" or "under served populations" or "under served world" or "deprived country" or "deprived countries" or "deprived nation" or "deprived nations" or "deprived population" or "deprived populations" or "deprived world" or "poor country" or "poor countries" or "poor nation" or "poor nations" or "poor population" or "poor populations" or "poor world" or "poorer country" or "poorer countries" or "poorer nation" or "poorer nations" or "poorer population" or "poorer populations" or "poorer world" or "developing economy" or "developing economies" or "less developed economy" or "less developed economies" or "lesser developed economy" or "lesser developed economies" or "under developed economy" or "under developed economies" or "underdeveloped economy" or "underdeveloped economies" or "middle income economy" or "middle income economies" or "low income economy" or "low income economies" or "lower income economy" or "lower income economies" or "low gdp" or "low gnp" or "low gross domestic" or "low gross national" or "lower gdp" or "lower gnp" or "lower gross domestic" or "lower gross national" or lmic or lmics or "third world" or "lami country" or "lami countries" or "transitional country" or "transitional countries")).tw.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% %%%
%%% Bibliography %%%

\clearpage
\newrefcontext[sorting=nyt]
\printbibliography

\end{document}

### 2024-07-22 manuscript.tex
Updates from Overleaf
Updated

@@
 Vaccines that are not cost-saving, but result in higher costs and higher health benefits, are often compared to country-specific willingness to pay thresholds, to determine whether an intervention is considered cost-effective (that is, of good value for money).
-Recent systematic reviews PCV is CE across (most)( LMICs (sometimes cost-saving) \supercite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}.
+Recent systematic reviews PCV is CE across (most)( LMICs (sometimes cost-saving) \autocite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}.
 Cost-effectiveness is influenced by vaccine price (local acquisition), inclusion/exclusion of indirect effects (serotype replacement and herd effects), cross protection, disease burden (Incidence / mortality from invasive pneumococcal disease (IPD), and pneumonia), and vaccine efficacy and coverage
@@
 Hence, they represented what the CMH believed governments should pay for improved health, rather than what interventions to choose given a fixed healthcare budget.
-They became widely cited and used to evaluate individual interventions, but WHO produced a paper advising against the use of GDP-based thresholds, especially in isolation from other considerations \parencite{bertram_costeffectiveness_2016}.
+They became widely cited and used to evaluate individual interventions, but WHO produced a paper advising against the use of GDP-based thresholds, especially in isolation from other considerations \autocite{bertram_costeffectiveness_2016}.
 Despite the World Health Organization and others recommending against using GDP per capita-based thresholds for judging the value for money of healthcare interventions most recent studies continue to do so4.
@@
 Newer country-specific estimates of cost-effectiveness thresholds (CETs) exist based on health opportunity costs are available.
-\supercite{ochalek_estimating_2018, pichon-riviere_determining_2023,woods_country-level_2016} New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
+\autocite{woods_country-level_2016, ochalek_estimating_2018, pichon-riviere_determining_2023} New approach to estimate threshold using empirical estimates of investments (supply side) or WTP (demand side).
 Several countries are in process of developing these thresholds (ex: Indonesia ).
-New estimates from \textcite{woods_country-level_2016} (based on one empirical estimate from a high-income setting), \textcite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs), and \textcite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
-\textcite{woods_country-level_2016} also provides these estimates for high-income countries.
+New estimates from \autocite{woods_country-level_2016} (based on one empirical estimate from a high-income setting), \autocite{ochalek_estimating_2018} (using multiple empirical data points, from LMICs), and \autocite{pichon-riviere_determining_2023} provide updated guidance on health opportunity costs in LMICs.
+\autocite{woods_country-level_2016} also provides these estimates for high-income countries.
 The main aim of this study is to investigate whether these estimates on cost-effectiveness thresholds (CET) based on health opportunity costs may impact on study conclusions about the cost-effectiveness of pneumococcal conjugate vaccine programs in low- and middle-income countries.
@@
 \section{Methods}
-\subsection{Systematic search}
-We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.\supercite{saokaew_cost_2016} We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-benefit OR cost-utility OR cost-effectiveness OR cost-benefit OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 25 April 2022.
+\subsection{Literature search strategy}
+We undertook a systematic literature search using similar search strings as a previous review on pneumococcal vaccination in children.\autocite{saokaew_cost_2016} We used the search strings “pneumococc* AND conjugat* AND (vaccin* OR immun*) AND “economic OR cost-effectiveness OR cost-utility” in the title, abstract, and keyword fields of Web of Science, Scopus, PubMed, and EmBase (Ovid) from inception until 17 July 2024.
 The search was limited to low- and middle-income countries (LMICs) using country names and related LMIC terminology (see Appendix 1 in Supplementary Material).
-We also checked published systematic reviews on economic evaluation of PCV for additional studies.\supercite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}
+We also checked published systematic reviews on economic evaluation of PCV for additional studies.\autocite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020}
 
+\subsection{Inclusion and exclusion strategy}
 All identified titles and abstracts were screened by one author (EA) to remove studies that were clearly not related to the topic, were not primary research, or not focused on a LMIC.
-Two reviewers (EA, NC) independently screened the full text of studies remaining against seven inclusion criteria: (1) original articles containing a full economic evaluation (two evaluations, costs and consequences ),5 (2) focused on one or more LMICs, (3) evaluated PCV covering seven or more serotypes, (4) evaluated PCV in children less than 12 years, (5) used either disability-adjusted life-years (DALYs), quality-adjusted life years (QALYs) or life-years (LY), as outcome measure, (6) reported an incremental cost-effectiveness ratio (ICER) and (7) were in English.
+Two reviewers (EA and NC) independently screened the full text of studies remaining against seven inclusion criteria: (i) original articles containing a cost-effectiveness or cost-utility analysis, (ii) focused on one or more LMICs, (iii) evaluated PCV covering seven or more serotypes, (iv) evaluated PCV in children less than 12 years, (v) used either disability-adjusted life-years (DALYs), quality-adjusted life years (QALYs) or life-years (LY), as outcome measure, (vi) reported an incremental cost-effectiveness ratio (ICER) and (vii) were written in English.
 Editorials, letters, conference or meeting abstracts or proceedings, and review articles were excluded.
@@
 
-The following data were extracted by one reviewer (EA) into an Excel data extraction template: study characteristics (country, currency and cost year, World Bank country income group, vaccine evaluated and comparator, number and unit price of doses); methodological assumptions of cost-effectiveness analysis (perspective (societal or healthcare payer), time horizon, discount rate, and considerations of herd effects (with or without) and serotype replacement (with or without)); and study results (outcome measure, ICER for each evaluation where this was separately reported (by perspective, and by inclusion or exclusion of herd effects and by serotype replacement, where possible), inclusion of budget impact (yes or no), cost-effectiveness threshold used and conclusion on cost-effectiveness, for each evaluation ).
+\subsection{Data extraction}
+The characteristics, methodological decisions, and results from each study were extracted by one reviewer (EA) into an Excel workbook.
+Study characteristics included the country, currency and cost year, World Bank country income group, type of vaccine evaluated (PCV7, PCV9, PCV10, or PCV13), and the number of doses.
+Countries were classified by World Bank country income group as upper middle (UM), lower middle (LM), and low (L) income.
+We then extracted information on the following parameters and methodological assumptions: study perspective (societal or healthcare/payer), time horizon, discount rate, and inclusion/exclusion of herd effects, inclusion/exclusion of serotype replacement, and unit price per vaccine used.
+We categorized the study results into cost-saving, cost-effective, or not-cost-effective.
+Where reported in a different currency, vaccine dose prices and ICERs were converted to United States dollars (USD) using year- and currency-specific exchange rates from the World Bank.6
+
+Most studies reported ICERs for more than one vaccine comparison or combination of methodological assumptions.
+For example, a study could report results for both PCV7 and PCV10 compared to no vaccination (NoVax), with and without including herd effects in both comparisons.
+This implies for that single study, there will be four evaluations (PCV7 vs NoVax with herd effects, PCV10 vs NoVax with herd effects, PCV7 vs NoVax without herd effects, and PCV10 vs NoVax without herd effects).
+Where this was the case, we extracted these ICERS and study characteristics in separate Excel rows.
+The extracted data was compared with data from published systematic reviews\autocite{saokaew_cost_2016, syeed_pneumococcal_2023, wang_systematic_2022, zakiyah_pneumococcal_2020} to verify the information on study characteristics, parameters, and ICERs.
 A second reviewer (NC) double-extracted one-third of studies.
 Any inconsistencies were discussed resolved in consultation with both reviewers.
-The extracted data was compared with data from published systematic reviews1-4 to verify the extracted data on study characteristics, parameters and ICERs.
+Risk of bias was not assessed as this has been done by previously published systematic reviews\textbf{2} and was not the focus of the current review.
 
-Risk of bias was not assessed as this has been done by previously published systematic reviews2 and was not the focus of the current review.
+% see https://www.tandfonline.com/doi/full/10.1080/14760584.2023.2173176
+\subsection{Cost-effectiveness threshold calculations}
+We updated the cost-effectiveness results for each evaluation from the studies as follows.
+First, we calculated the ICER as a \% of GDP per capita by dividing each ICER by the country- and year-specific GDP per capita from The World Bank \autocite{the_world_bank_gdp_2023}.
+Next, we extracted country-specific highest and lowest CET estimates from the three studies \autocite{woods_country-level_2016, ochalek_estimating_2018, pichon-riviere_determining_2023}.
+We then converted these CETs to equivalent \% GDP per capita, using the year-specific GDP per capita \autocite{the_world_bank_gdp_2023}: 2013 for Woods\autocite{woods_country-level_2016} and 2019 for P-Riverie\autocite{pichon-riviere_determining_2023}.
+The CET as \% GDP per capita was obtained directly from Ochalek\autocite{ochalek_estimating_2018}.
+Finally, we then generated updated study conclusions (“cost-effective” or “not-cost-effective) for each evaluation according to the Woods and Ochalek CETs, by comparing the converted ICER (in \% GDP per capita) to the upper- and lower-bound CETs (in \% GDP per capita ).
+The results of cost-saving evaluations remained unchanged as they do not depend on the CET value.
 
-\subsection{Data preparation}
-Countries were classified by World Bank country income group as upper middle (UM), lower middle (LM), and low (L) income.
-Where reported in a different currency, ICERs and vaccine dose prices were converted to United States dollars (USD) using year- and currency-specific exchange rates from the World Bank.6 Country- and year-specific GDP per capita estimates (in USD) were compiled from World Bank data and used to convert ICERs for all evaluations into a \% GDP per capita.
-We extracted country-specific upper- and lower-bound CETs from the Woods7 and Ochalek8 studies, in terms of \% GDP per capita, using the highest and lowest estimates from both studies.
-We then generated updated study conclusions (“cost-saving”, “cost-effective” or “not-cost-effective) for each evaluation according to the Woods and Ochalek CETs, by comparing the converted ICER (in \% GDP per capita) to the upper- and lower-bound CETs (in \% GDP per capita ).
-We generated four indicator variables to indicate whether study conclusions shifted from being “cost-effective” based on study specific threshold and conclusion, to “not cost-effective” (based on each of the four updated CET estimates: WoodsHigh, WoodsLow, OchalekHigh, OchalekLow).
-Studies where CETs were not explicitly stated were not included in the statistical analysis.
+ We generated six indicator variables to record whether study conclusions shifted from being “cost-effective” based on study-specific threshold and conclusion, to “not cost-effective”.
+These variables were based on each of the updated CET estimates: Woods (2016) High value, Woods (2016) Low value, Ochalek (2018) High value, Ochalek (2018) Low value, P-Rivere (2023) High value, and P-Rivere (2023) High value.
+We also generated an "any switch" variable, to indicate switching from being cost-effective to not-cost-effective across any of the six CET estimatess.
+to for  Studies where CETs were not explicitly stated were excluded from the statistical analysis.
 
@@
 We first summarised the key characteristics of studies and unique evaluations included in the review including distribution of CETs used and study conclusions.
-We then conducted a descriptive analysis of the evaluations that switched from being considered “cost-effective” by the study conclusion to “not cost-effective” (across any of the 4 CETs), by study perspective, type of comparison, income group, considerations of herd effects or serotype replacement, vaccine dose price by income group.
-
-Next, we conducted two-sample tests of differences in vaccine dose price, country income group, perspective of analysis, and considerations of herd immunity  or serotype replacement among evaluations that switched from being cost-effective across any of the 4 CETs, compared to those that didn’t switch.
+We then conducted a descriptive analysis of the evaluations that switched from being considered “cost-effective” by the study conclusion to “not cost-effective” (across any of the six CETs), by study perspective, type of comparison, income group, considerations of herd effects or serotype replacement, vaccine dose price by income group.
+Next, we conducted statistical tests for differences among evaluations that switched from being cost-effective across any of the six CETs, compared to those that didn’t switch.
+The tests used were two-sample tests for differences in vaccine dose price, and Fisher's exact test for differences by country income group, perspective of analysis, and inclusion of herd immunity or serotype replacement.
 
@@
 \clearpage
-\newrefcontext[sorting=nyt]
 \printbibliography

### 2024-07-22 code/analysis.R
Updated

@@ -9,6 +9,9 @@ library(kableExtra)
 # Import studies from folder
 studies <- read.csv("data/studies.csv", row.names=NULL, stringsAsFactors=TRUE)
 
+
+#studies <- readxl::read_excel("data/studies.xlsx", sheet = "studies")
+
 Include = c("comparison", "doseNum", "perspective", "income", "herdEffects", 
             "seroReplace", "efficacyPneum", "efficacyIPD", "efficacyOtitis", 
             "budgetImpact", "studyDecide")

### 2024-07-22 code/analysis.R
Update analysis.R

@@ -7,10 +7,10 @@ library(scales)
 library(kableExtra)
 
 # Import studies from folder
-studies <- read.csv("data/studies.csv", row.names=NULL, stringsAsFactors=TRUE)
+#studies <- read.csv("data/studies.csv", row.names=NULL, stringsAsFactors=TRUE)
 
 
-#studies <- readxl::read_excel("data/studies.xlsx", sheet = "studies")
+studies <- readxl::read_excel("data/studies.xlsx", sheet = "studies")
 
 Include = c("comparison", "doseNum", "perspective", "income", "herdEffects", 
             "seroReplace", "efficacyPneum", "efficacyIPD", "efficacyOtitis", 
@@ -71,7 +71,7 @@ df <- tbl_merge(list(df1, df2), tab_spanner=FALSE) %>%
   as_kable_extra(, format = "latex", escape = FALSE) %>%
   gsub(".(begin|end){tabular.*}", "", ., perl = TRUE) %>% # remove tabular
   sub("\\\\hline", "", .)  # remove the first hline
-writeLines(df, "output/tables/tab_evals_studies.tex")
+writeLines(df, "tables/tab_evals_studies.tex")
 rm(df1, df2, df)
 
 
@@ -105,7 +105,7 @@ df <- add_header_above(df, c(" ", " ", " ", "Ochalek (2018)" = 2,
                        border_left = T, border_right = T) %>% 
   gsub(".(begin|end){tabular.*}", "", ., perl = TRUE) %>% # remove tabular
   sub("\\\\hline", "", .)  # remove the first hline
-writeLines(df, "output/tables/tab_evals_thresholds.tex")
+writeLines(df, "tables/tab_evals_thresholds.tex")
 
 
 
@@ -124,91 +124,89 @@ studies <- studies %>%
                                TRUE ~ 0))
 
 
+# # Create contingency table with frequencies
+# f.Switch <- function(typeVar, switchVar){
+#   data = studies[studies$comparison!="Others", ]
+#   data = droplevels(data)
+#   x = table(data[[typeVar]], data[[switchVar]])
+#   switchProp = prop.table(x, margin = 1) * 100
+#   return(list(typeVar = typeVar,
+#               switchVar = switchVar,
+#               level = rownames(switchProp)[which.max(switchProp[, "1"])], 
+#               max   = round(max(switchProp[, "1"]), 1), 
+#               `p-value` = round(fisher.test(x)$p, 3)))
+# }
+# 
[…]

### 2024-07-22 code/analysis.R
Updated

@@ -108,21 +108,140 @@ df <- add_header_above(df, c(" ", " ", " ", "Ochalek (2018)" = 2,
 writeLines(df, "tables/tab_evals_thresholds.tex")
 
 
-
-
-# Make "new_switches" variable that is only relevant to evaluations that switch from being cost-effective (not "cost-saving" or "not cost-effective")
+# Make "anySwitch" variable for switching based on any threshold
 studies <- studies %>%
-  mutate(new_switches = case_when(switches==0 & studyDecide=="Cost-saving" ~ NA,
-                                  switches==0 & studyDecide=="Not cost-effective" ~ NA,
-                                  TRUE ~ switches),
-         anySwitch = case_when(is.na(new_switches) ~ NA, 
-                               new_switches!=0 ~ 1,
-                               TRUE ~ 0),
-         # Natalie analysis
-         anySwitch2 = case_when(is.na(new_switches) ~ 1, 
-                               new_switches!=0 ~ 1,
-                               TRUE ~ 0))
+  mutate(anySwitch = case_when(is.na(switches) ~ NA, switches!=0 ~ 1, TRUE ~ 0))
 
+
+# Create contingency table with frequencies
+f.Switch <- function(typeVar){
+  data = studies[studies$comparison!="Others", ]
+  data = droplevels(data)
+  x = table(data[[typeVar]], data[["anySwitch"]])
+  switchProp = prop.table(x, margin = 1) * 100
+  return(list(typeVar = rep(typeVar, length(levels(data[[typeVar]]))),
+              level = rownames(switchProp),
+              switchProp = round(switchProp[, "1"], 1),
+              `p-value` = rep(round(fisher.test(x)$p, 3), 
+                              length(levels(data[[typeVar]])))))
+}
+
+studies$herdEffects = factor(studies$herdEffects)
+studies$seroReplace = factor(studies$seroReplace)
+studies$income      = factor(studies$income)
+studies$perspective = factor(studies$perspective)
+
+df <- rbind(data.frame(f.Switch("comparison")),
+            data.frame(f.Switch("income")),
+            data.frame(f.Switch("herdEffects")),
+            data.frame(f.Switch("seroReplace")),
+            data.frame(f.Switch("perspective")))
[…]

### 2024-08-01 manuscript.tex
Updates from Overleaf

@@
 No relationship was found between perspective of analysis and the evaluation switching from begin cost-effective.
-However, evaluations that switched from being cost-effective to not cost-effective across any of the new CETs had statistically higher mean vaccine dose price: \$31.82 (\$26.73-\$36.91) vs \$15.41 (\$7.26-\$23.55).
+However, evaluations that switched from being cost-effective to not cost-effective across any of the new CETs had statistically higher mean vaccine dose price: \$27.7  vs \$15.5 (mean difference \$12.2, 95\% confidence interval, 2.9 to 21.4).
+
 Probit regression results found vaccine dose price and country income group were the only statistically significant variables related to evaluations switching from being cost-effective to not cost-effective across any one of the updated CETs.
@@
     \centering \singlespacing \small
-    \caption{Characteristics of included evaluations and unique studies}
+    \caption{Likelihood of switching}
     \begin{tabular}{|L{4.5cm}|L{4cm}|C{2.75cm}|C{2.75cm}|}
